On Secure Delegation of SampBQP with a Classical Client

### 2020-03-22 qpip.tex
Fix typos and add TODOs

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $O(\poly(\varepsilon))$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$, $\delta=2h$ to get
	$$\Prob{\frac{m}{2}-Z\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$

@@

	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2h$,
	then clearly $\Prob{Z\geq\frac{m}{2}-hm}<\Prob{Y\geq\frac{m}{2}-hm}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-hm}=\Prob{Y-\mu\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
	where $\mu=mp_y=\frac{m}{2}-2hm$ and $\delta=\frac{2h}{1-4h}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda)$$

	Now, for the other case, $j\notin J$.
	$$\Prob{\cV_\GS(\phi)=acc}>\frac{1}{2}-2h\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\poly(\varepsilon)$$
	we then have
	$$\braket{\rho_i|H_{C'(x)}|\rho_i}<\poly(\varepsilon).$$
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain
	$$\braket{\rho_i|\phi_{C'(x)}}>1-\poly(\varepsilon).$$
	By a standard fidelity argument, the measurement results on $\rho_i$ is $\poly(\varepsilon)$-close to that on $\ket{\phi_{C'(x)}}$.

@@

	The soundness errors incurred at each step is at most $\poly(\varepsilon)$, so the conclusion follows.
\end{prf}

>>>>

\begin{thm}
    \label{QPIP1thm}
	$\PiSamp$ has negligible completeness error and $\poly(\varepsilon)$ soundness error.
\end{thm}
\begin{prf}
	For completeness, notice $z_i$ are i.i.d. Bernoulli trials with success probability $\frac{1}{2}$.
	So we can apply the Chernoff bound \cref{thm:Chernoff} with $\mu=\frac{m}{2}$, $\delta=2h$ to get
	$$\Prob{\frac{m}{2}-Z\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$

@@

	First suppose $j\in J$, we use a standard Chernoff bound argument as follows to show that this case has negligible acceptance probabilities,
	hence incurs negligible soundness errors.
	Let $Y=\sum y_j$ be i.i.d. Bernoulli trials with success probabilities $p_y=\frac{1}{2}-2h$,
	then clearly $\Prob{Z\geq\frac{m}{2}-hm}<\Prob{Y\geq\frac{m}{2}-hm}$.
	By Chernoff bound, we have
	$$\Prob{Y\geq\frac{m}{2}-hm}=\Prob{Y-\mu\geq hm}\leq2e^{-\frac{\mu\delta^2}{3}}=\negl(T)$$
	where $\mu=mp_y=\frac{m}{2}-2hm$ and $\delta=\frac{2h}{1-4h}$.
	Summing up all the $\rho_j$ terms in $J$, we have
	$$\sum_{j\in J} w_j q_j<2^{-\lambda}=\negl(\lambda).$$

	Now, for the other case, $j\notin J$.
	$$\Prob{\cV_\GS(\phi)=acc}>\frac{1}{2}-2h\Rightarrow\braket{\phi|H_{C'(x)}|\phi}<\poly(\varepsilon)$$
	we then have
	\Ethan{$\rho_j$ isn't a pure state, so need to rewrite this using traces and such}
	$$\braket{\rho_j|H_{C'(x)}|\rho_j}<\poly(\varepsilon).$$
	We also know that the least nonzero eigenvalue of $H_{C'(x)}$ is lower-bounded by $\frac{3}{4}$, so we obtain
	$$\braket{\rho_j|\phi_{C'(x)}}>1-\poly(\varepsilon).$$
	By a standard fidelity argument, the measurement results on $\rho_j$ is $\poly(\varepsilon)$-close to that on $\ket{\phi_{C'(x)}}$.

@@

	The soundness errors at each step is $\poly(\varepsilon)$, so the conclusion follows.
\end{prf}
